Magnetic Inhibition of Convection and the Fundamental Properties of Low--Mass Stars

### 2016-03-02 paper/ms.tex
revising discussion

{\bf Figure~\ref{fig:ages} shows that a 10 Myr magnetic model isochrones traces a 5 Myr standard model isochrone for effective temperatures below about 5\,000~K, but traces a 10 Myr standard model isochrone above 6\,000~K. This suggests that magnetic inhibition plays an important role in dictating the structure of cool low-mass stars, but the structure of warmer high-mass stars are relatively insensitive to the influence of magnetic fields. In between these two regimes, the models predict a that a transition occurs in which stars appear to exhibit an increasing sensitivity to magnetic inhibition of convection as effective temperature decreases.

As was noted in Sect.~\ref{sec:results}, Figs.~\ref{fig:empirical} and \ref{fig:ages}a indicate that this transition occurs over a similar effective temperature domain in the HR diagram of Upper Scorpius. Early- to mid-G stars in Upper Scorpius (\teff$ \sim 6000$~K) are best described by a 10 Myr standard stellar model isochrone. Instead of continuing to follow a 10 Myr isochrone, late-G stars appear to be better represented by an isochrone intermediate between 5 and 10 Myr causing the empirical sequence to exhibit a shallower slope than standard model predictions between $5750 > T_{\rm eff} / {\rm K} > 5000$~K. Agreement between the transition region observed in the empirical data and the one predicted by magnetic stellar models suggests there is a physical explanation for the observed transition, but might there be an alternative explanation?
}

@@

{\bf The transition region observed in the HR diagram appears to be the result of a real transition in which the structure of stars becomes increasingly insensitive to magnetic inhibition of convection toward higher temperatures. Comparison of the empirical HR diagram to magnetic stellar models suggests that the transition's effective temperature domain begins somewhere between 4\,500~K and 5\,000~K, consistent with the knee observed in the empirical data at \teff$\sim 4\,500$~K. According to magnetic stellar models, these effective temperatures correspond to stars with masses between 1.26 \msun\ and 1.40 \msun. This is significant because stars in this mass regime are expected to have relatively thin convective envelopes that eventually disappear entirely. 
}

>>>>

{\bf Figure~\ref{fig:ages} shows that a 10 Myr magnetic model isochrones traces a 5 Myr standard model isochrone for effective temperatures below about 5\,000~K, but traces a 10 Myr standard model isochrone above 6\,000~K. This suggests that magnetic inhibition plays an important role in dictating the structure of cool low-mass stars, but the structure of warmer high-mass stars are relatively insensitive to the influence of magnetic fields. In between these two regimes, the models predict a that a transition occurs in which stars appear to exhibit an increasing sensitivity to magnetic inhibition of convection as effective temperature decreases. }

{\bf As was noted in Sect.~\ref{sec:results}, Figs.~\ref{fig:empirical} and \ref{fig:ages}a indicate that a similar transition occurs over roughly the same effective temperature domain in the empirical HR diagram of Upper Scorpius. Early- to mid-G stars in Upper Scorpius (\teff$ \sim 6\,000$~K) are best described by a 10 Myr standard stellar model isochrone. Instead of continuing to follow a 10 Myr standard model isochrone, late-G stars appear to be better represented by an isochrone intermediate between 5 and 10 Myr causing the empirical sequence to exhibit a shallower slope than standard model predictions between $5\,750 > T_{\rm eff} / {\rm K} > 4\,500$~K. 
That the shallower slope in the empirical HR diagram and the transition predicted by magnetic stellar models are coincident, suggests that the two phenomena may be connected.
}

{\bf The transition exhibited by theoretical magnetic models can be explained by the rapid thinning of outer convective envelopes in stars with masses above about 1.2 $M_{\odot}$.
Once a star reaches an effective temperature of 6\,000 K, it has either a very small or non-existent convective envelope. This provides a natural explanation the convergence of the 10 Myr magnetic isochrone with the 10 Myr standard model isochrone that occurs near this effective temperature in Fig.~\ref{fig:ages}(b).

Assuming that a change in slope of the empirical HR diagram is observed at 4\,500 K, 
Comparison of the empirical HR diagram to magnetic stellar models suggests that the transition's effective temperature domain begins somewhere between 4\,500~K and 5\,000~K, consistent with the knee observed in the empirical data at \teff$\sim 4\,500$~K. According to magnetic stellar models, these effective temperatures correspond to stars with masses between 1.26 \msun\ and 1.40 \msun. This is significant because stars in this mass regime are expected to have relatively thin convective envelopes that eventually disappear entirely. 
}

@@
